PANCHANGE_data_preprocessing

### 2020-08-18 PANCHANGE_data_preprocessing2020-07-15.Rmd
edits to age respiratory variable

Age is not available in RAMP, only categorical age. We will assign each individual the middle value of each age category. 
```{r create age - proxy variable for ramp}
if(RAMP == TRUE){
dat.coping <- dat.coping %>%
  mutate(
    Age =
      case_when(
        age_category_full == "16-18" ~ 17,
        age_category_full == "19-25" ~ 22,
        age_category_full == "26-35" ~ 30.5,
        age_category_full == "36-45" ~ 40.5,
        age_category_full == "46-55" ~ 50.5,
        age_category_full == "56-65" ~ 60.5,
        age_category_full == "66-70" ~ 68,
        age_category_full == "71-75" ~ 73,
        age_category_full == "76-80" ~ 78,
        age_category_full == "81-85" ~ 83,
        age_category_full == "86-90" ~ 88,
        age_category_full == "91-100" ~ 93,
      age_category_full == "100+" ~ 100
      )
  )
}
```

@@

#COVID prediction model
```{r COVID prediction model}
# linear model of covid symptoms
dat.coping <- dat.coping %>%
		  mutate(
		    covid_probability = 
		      (-1.32) - 
		      (0.01*Age) + 
		      (0.44*Sex_respiratory) + 
		      (1.75*respiratory.anosmia_binary) + 
		      (0.31*respiratory.pcough_binary) +  
		      (0.49*respiratory.fatigue_binary) +  
		      (0.39*respiratory.skipped_meals_binary) 
		         )

# Calcualte the odds ratios 
dat.coping <- dat.coping %>%
  mutate(
    covid_odds_ratio = 
      (exp(covid_probability) / (1 + exp(covid_probability)))
  )

# generate binary cutt off variable for risk of COVID 
dat.coping <- dat.coping %>%
		  mutate(
		    covid_odds_ratio_50_numeric = 
		      case_when(
		        covid_odds_ratio >= 0 & covid_odds_ratio < 0.5 ~ "0", #cut off at 0.5 
		        covid_odds_ratio >= 0.5 & covid_odds_ratio <= 1 ~ "1"
		      )
		  )

>>>>

Age is not available in RAMP, only categorical age. We will assign each individual the middle value of each age category. 
```{r create age - proxy variable for ramp}
if(RAMP == TRUE){
dat.coping <- dat.coping %>%
  mutate(
    Age_respiratory =
      case_when(
        age_category_full == "16-18" ~ 17,
        age_category_full == "19-25" ~ 22,
        age_category_full == "26-35" ~ 30.5,
        age_category_full == "36-45" ~ 40.5,
        age_category_full == "46-55" ~ 50.5,
        age_category_full == "56-65" ~ 60.5,
        age_category_full == "66-70" ~ 68,
        age_category_full == "71-75" ~ 73,
        age_category_full == "76-80" ~ 78,
        age_category_full == "81-85" ~ 83,
        age_category_full == "86-90" ~ 88,
        age_category_full == "91-100" ~ 93,
      age_category_full == "100+" ~ 100
      )
  )
}

if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE){
dat.coping <- dat.coping %>%
  mutate(
    Age_respiratory = Age
  )
}
```

@@

#COVID prediction model
```{r COVID prediction model}
# linear model of COVID symptoms
dat.coping <- dat.coping %>%
		  mutate(
		    covid_probability = 
		      (-1.32) - 
		      (0.01*Age_respiratory) + 
		      (0.44*Sex_respiratory) + 
		      (1.75*respiratory.anosmia_binary) + 
		      (0.31*respiratory.pcough_binary) +  
		      (0.49*respiratory.fatigue_binary) +  
		      (0.39*respiratory.skipped_meals_binary) 
		         )

# Calculate the odds ratios 
dat.coping <- dat.coping %>%
  mutate(
    covid_odds_ratio = 
      (exp(covid_probability) / (1 + exp(covid_probability)))
  )

# generate binary cut off variable for risk of COVID 
dat.coping <- dat.coping %>%
		  mutate(
		    covid_odds_ratio_50_numeric = 
		      case_when(
		        covid_odds_ratio >= 0 & covid_odds_ratio < 0.5 ~ "0", #cut off at 0.5 
		        covid_odds_ratio >= 0.5 & covid_odds_ratio <= 1 ~ "1"
		      )
		  )
